---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# binomial

The goal of the `"binomial"` package is to provide functions for calculating the properties of the binomial random variable, including:  
- `bin_variable()` creates a binomial variable when given `n` trials and `p` probability  

- `bin_probability()` calculates the probability of getting `k` successes out of `n` trials with a probability `p`  

- `bin_distribution()` outputs a data frame of the binomial distribution of `n` trials given a probability of `p`  

- `bin_cumulative()` outputs a data frame of cumulative binomial distribution given a `n` trials and a probability of `p`  

- `bin_mode()`, `bin_mean()`, `bin_variance()`, `bin_skewness()`, `bin_kurtosis()` are summary measures

## Installation

You can install the released version of Binomial03 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("binomial")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat133-sp19/hw-stat133-yangluanne/binomial")
```
## Example

This is a basic example which shows you how to solve a common problem:
```{r example}
library(binomial)

# binomial random variable
X <- bin_variable(trials = 5, prob = 0.5)
X

# binomial probability
bin_probability(success = 2, trials = 5, prob = 0.5)

# binomial distribution
dist <- bin_distribution(trials = 5, prob = 0.5)
dist

# binomial ditribution plot
plot(dist)

# binomial cumulative distribution
cumu <- bin_cumulative(trials = 5, prob = 0.5)
cumu

# binomial cumulative distribution plot
plot(cumu)

# binomial random variable summary statistics
summary(X)

# summary measures
bin_mean(5, 0.5)
bin_variance(5, 0.5)
bin_mode(5, 0.5)
bin_skewness(5, 0.5)
bin_kurtosis(5, 0.5)

```
