---
title: "Introduction to Binomial Package"
author: "Luanne Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VigneteEncoding{UTF-8}
---

kill DESCRIPTION and hello.Rd
 use devtools::document() in console
 use devtools::check_man() in console to check that the man file is ok
  want to see "no issues detected"
 use devtools::tests() to run tests
 use devtools::build() to build the package
```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Distribution
The binomial distribution is a probability model that is used to calculate probabilities about the number of successes in a fixed number of random yet identical trials.

The `"binomial"` package includes functions for calculating probabilities of a Binomial random variable and related properties including:
* expected value
* variance
* mode
* skewness
* kurtosis
* binomial distribution
* cumulative probabilities
* plots

## Binomial Probability  

Suppose we have a fair coin that is either heads or tails. Let \(X =\)flipping the fair coin 5 times.

## Creating a Binomial Variable

To create a binomial variable object, use the `bin_variabe()` function.

```{r}
X <- bin_variable(5, 0.5)
X
```  
```{r}
summary(X)
```


We can use the `bin_probability()` function to find the probability of getting 2 heads out of 5 flips.
```{r}
bin_probability(2, 5, 0.5)
```

## Mean   

To find the expected value of \(X\), we can use the `bin_mean()` function.
```{r}
bin_mean(5, 0.5)
```  

## Variance

To find the variance of \(X\), we can use the `bin_variance()` function.
```{r}
bin_variance(5, 0.5)
```

## Mode  

The most likely number of success in 5 independent flips of a fair coin can be found with `bin_mode()`.
```{r}
bin_mode(5, 0.5)
```


## Skewness  

Skewness is a measure of the asymmetry of the probability distribution of a random variable about its mean. To find the skewness of \(X\), we can use the `bin_skewness()` function.
```{r}
bin_skewness(5, 0.5)
```  

## Kurtosis  

The Kurtosis is a measure of the "tailedness" of the probability distribution of a random variable. To find the kurtosis of \(X\), we can use the `bin_kurtosis()` function.
```{r}
bin_kurtosis(5, 0.5)
```




```{r}
bin_distribution(5, 0.5)
```



